PAPER TEMPLATE FOR ISMIR 2014

### 2014-04-27 paper/paper.tex
typo

In the measure definitions provided above, it is assumed that both the estimate
and reference sequences are sampled using the same time grid (hop size). In
practice, however, this is not always the case, since the time grid of the
reference depends on the hop size used by the pitch tracker that produced
it, and similarly the time grid of the estimate depends on the specific melody
extraction algorithm that produced it. This means that the sequences must be
resampled onto a common time-grid prior to the computation of the measures. For
the MIREX AME task, any sequence (be it reference or estimate) that is not
sampled using a 10 ms hop size is resampled using $0^{th}$ order interpolation,
i.e.~each frequency value in the target sequence is set to its nearest
neighbour (in time) from the source sequence. This kind of interpolation can
potentially have a detrimental effect on the evaluation, depending on the
difference between the source and target time grids. In particular, it can
result in artificially low scores for sequences with rapidly changing pitch
values, such as opera singing with deep vibrato.

For this reason, the melody evaluator in mir\_eval uses $1^{st}$ order (linear)
interpolation by default in order to map the reference and estimate sequences
onto a common time-grid. Assuming the original timestamps of both sequences
correspond to the \textit{center} of each analysis frame (as they should),
using $1^{st}$ order rather than $0^{th}$ order interpolation means the results
returned by mir\_eval are lower-bounded by the MIREX results and are, in our
view, more accurate.

>>>>

In the measure definitions provided above, it is assumed that both the estimate
and reference sequences are sampled using the same time grid (hop size). In
practice, however, this is not always the case, since the time grid of the
reference depends on the hop size used by the pitch tracker that produced
it, and similarly the time grid of the estimate depends on the specific melody
extraction algorithm that produced it. This means that the sequences must be
resampled onto a common time-grid prior to the computation of the measures. For
the MIREX AME task, any sequence (be it reference or estimate) that is not
sampled using a 10 ms hop size is resampled using $0^{th}$-order interpolation,
i.e.~each frequency value in the target sequence is set to its nearest
neighbour (in time) from the source sequence. This kind of interpolation can
potentially have a detrimental effect on the evaluation, depending on the
difference between the source and target time grids. In particular, it can
result in artificially low scores for sequences with rapidly changing pitch
values, such as opera singing with deep vibrato.

For this reason, the melody evaluator in mir\_eval uses $1^{st}$-order (linear)
interpolation by default in order to map the reference and estimate sequences
onto a common time-grid. Assuming the original timestamps of both sequences
correspond to the \textit{center} of each analysis frame (as they should),
using $1^{st}$-order rather than $0^{th}$-order interpolation means the results
returned by mir\_eval are lower-bounded by the MIREX results and are, in our
view, more accurate.
